Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-13 Response.tex

-Transfers are 2D only, method is more challenging to adapt to 3D

-Presented control magnitudes are dimensionally large, and more work is needed to determine feasibility of approach for lower accelerations

-Thrust and mass are completely decoupled from the analysis, which is limiting in terms of finding suitable hardware that can deliver the controls needed, as currently presented.
\end{itshape}

The conclusion has been expanded with some discussion of the drawbacks of this research and avenues of future work.
The modified conclusion is copied below.

\begin{correction}
In this paper, an optimal transfer process which combines concepts of reachability and \Poincare section is used to generate transfer between planar periodic orbits in the three-body problem.
The \Poincare section allows for trajectory design on a lower dimensional phase space and simplifies the process.
The indirect optimal control formulation enables straightforward method of incorporating additional path and control constraints.
However, the use of optimal control techniques leads to open loop trajectories that are not robust to model uncertainties or disturbances.
Furthermore, our approach relies heaviliy on the relative simplicity of the PCRTBP and this method is much more challenging for the non-planar case.

There is additional research to extend these results to more general transfer scenarios in future work.
The incorporation of fourth body perturbations, such as the Sun in the Earth-Moon system, offers an additional method of increasing the reachable set with the combined use of the solar perturbation and low-thrust propulsion.
In addition, the assumed acceleration magnitude is currently beyond the capabilities of current electric propulsion systems.
Furthermore, this analysis did not consider the effect of variable mass on the optimal control solution.
This will result in a more complicated optimal control problem and is a focus of future research.
Finally, Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
The addition of attitude dynamics and realistic pointing constraints would significantly improve the applicability of this work.
\end{correction}
\end{enumerate}
\section*{Reviewer 2}

### 2017-07-13 Response.tex

\begin{correction}
The numerical examples presented in this section are designed in the context of the PCRTBP.
The dynamic environment has a four dimensional state space and offers a convient integration constant in the form of the Jacobi integral.
As a result, there are well defined methods to define and exploit \Poincare sections, which result in straightforward two-dimensional subspaces of the system.
Our approach uses the \Poincare section to approximate the reachability set on this reduced subspace.
As a result, this approach is more difficult to apply to three-dimensional transfers in the general three body problem.
\Poincare sections in the case of the general six dimensional state space are significantly more challenging and typically require more complicated visualization techniques. 
However, this is an area of active research and some of the authors future research is aimed at implementing this approach for non-planar transfer trajectories.
\end{correction}

\item
    \begin{itshape}
Figures 10D and 13D - the authors need to present these plots in dimensional coordinates so that they may be reconciled with what existing technology can produce.  I recommend Newtons or milliNewtons.  For example, the NEXT (NASA evolutionary xenon thruster) can produce 0.25 Newtons of thrust at maximum power (~7 kW).  The XR5 Hall thruster can produce comparable thrust at 4.5 kW of power.  These are currently the highest-power single engines other than the ARM Hall thruster which is not flight ready yet.  For these examples to be reconciled against the capability of existing technology, we need to see the required forces that are being demanded from the optimal control problem.  It may be that the results are beyond the scope of current technology - that's fine - just say that they are examples and that it's ongoing work to formulate example problems that capture existing technology better.
\end{itshape}

The mentioned plots of the control input have been modified to show the data in dimensional units (Newtons). 
Some additional detail has been provided in the manuscript which discusses the choice of \( u = 0.75 \) and it's realtionship to the current state of the art thruster systems.
The modified plots are not included here but the additional content is copied below in response to a different but related comment.

### 2017-07-13 manuscript.tex

\section{Conclusions}\label{sec:conclusion}
In this paper, an optimal transfer process which combines concepts of reachability and \Poincare section is used to generate transfer between planar periodic orbits in the three-body problem.
The \Poincare section allows for trajectory design on a lower dimensional phase space and simplifies the process.
The indirect optimal control formulation enables straightforward method of incorporating additional path and control constraints.
However, the use of optimal control techniques leads to open loop trajectories that are not robust to model uncertainties or disturbances.
Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
This analysis has also assumed perfect attitude control and the ability to orient thrust in any direction.
The addition of attitude dynamics and realistic pointing constraints would significantly improve the applicability.

>>>>

\section{Conclusions}\label{sec:conclusion}
In this paper, an optimal transfer process which combines concepts of reachability and \Poincare section is used to generate transfer between planar periodic orbits in the three-body problem.
The \Poincare section allows for trajectory design on a lower dimensional phase space and simplifies the process.
The indirect optimal control formulation enables straightforward method of incorporating additional path and control constraints.
However, the use of optimal control techniques leads to open loop trajectories that are not robust to model uncertainties or disturbances.
Furthermore, our approach relies heaviliy on the relative simplicity of the PCRTBP and this method is much more challenging for the non-planar case.

There is additional research to extend these results to more general transfer scenarios in future work.
The incorporation of fourth body perturbations, such as the Sun in the Earth-Moon system, offers an additional method of increasing the reachable set with the combined use of the solar perturbation and low-thrust propulsion.
In addition, the assumed acceleration magnitude is currently beyond the capabilities of current electric propulsion systems.
Furthermore, this analysis did not consider the effect of variable mass on the optimal control solution.
This will result in a more complicated optimal control problem and is a focus of future research.
Finally, Lyapunov control theory, which has previously been applied to the two-body problem, is being investigated in the hope of designing closed loop control schemes for this three-body scenario~\cite{chang2002}.
The addition of attitude dynamics and realistic pointing constraints would significantly improve the applicability of this work.
